---
title: "Flexdashboard UNMSM"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tm)
library(wordcloud)
library(readr)
```

```{r datasets}
videos <- read_csv("C:/Users/diego/Desktop/Progra/flex/material/academatica_videos.csv")
metadata <- read_csv("C:/Users/diego/Desktop/Progra/flex/material/academatica_videos_metadata.csv")
stats <- read_csv("C:/Users/diego/Desktop/Progra/flex/material/academatica_video_stats.csv")
```

```{r kpis}
metricas <- stats %>% 
  summarise(total_views = sum(viewCount),
            total_likes = sum(likeCount),
            total_dislike = sum(dislikeCount),
            total_favorite = sum(favoriteCount),
            total_comments = sum(commentCount))
```

# metricas {data-icon=fa-ruler}
##
### Reproducciones

```{r}
valueBox(formattable::comma(metricas$total_views,digits=0),icon = 'fa-eye',color = "success")
```

### Likes

```{r}
valueBox(formattable::comma(metricas$total_likes,digits=0),icon = 'fa-thumbs-up',color = "warning")
```

### Comentarios

```{r}
valueBox(formattable::comma(metricas$total_comments,digits=0),icon = 'fa-comment',color = "danger")
```

##
### Porcentaje de likes

```{r}
likes_rate <- metricas$total_likes/(metricas$total_likes+metricas$total_dislike)
likes_rate <- round(likes_rate*100,0)
gauge(likes_rate, min = 0, max= 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Porcentaje de dislikes

```{r}
dislikes_rate <- metricas$total_dislike/(metricas$total_likes+metricas$total_dislike)
dislikes_rate <- round(dislikes_rate*100,0)
gauge(dislikes_rate, min = 0, max= 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


##
### Total videos subidos por año y mes

```{r}
videos %>% 
  mutate(year = year(ymd_hms(contentDetails.videoPublishedAt)),
         month = month(ymd_hms(contentDetails.videoPublishedAt),label = TRUE),
         year = as.factor(year)) %>% 
  group_by(year, month) %>% 
  summarise(uploaded_videos = n_distinct(id)) %>%
  ggplot(aes(x=month,
             y=uploaded_videos,
             fill=year))+
  geom_col(position = 'dodge')
```

# Data {data-icon="fa-database"}
## {.tabset}
### wordcloud
```{r}
docs <- Corpus(VectorSource(metadata$title))
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "-")
docs <- tm_map(docs, toSpace, "\\(")
docs <- tm_map(docs, toSpace, "\\)")
docs <- tm_map(docs, toSpace, "\\|")

docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, removeWords, stopwords("spanish"))
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("video", 
                                    "problema",
                                    "ejemplo",
                                    "parte",
                                    "ejercicio",
                                    "ejercicios",
                                    "ejemplos")) 
docs <- tm_map(docs, removePunctuation)
docs <- tm_map(docs, stripWhitespace)
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=100, random.order=TRUE, rot.per=0.1, 
          colors=brewer.pal(8, "Dark2"))
```

### table 
```{r}
stats %>% 
  mutate(hasLike = if_else(likeCount>0,"si","no" )) %>% 
  filter(hasLike == 'no') %>% 
  left_join(metadata, by = c("id"="video_id")) %>% 
  select(id,title) %>%
  DT::datatable()
```

# statistics {data-icon="fa-chart-bar"}
### Lung Deaths (All)

```{r}
library(plotly)

mtcars$am[which(mtcars$am == 0)] <- 'Automatic'
mtcars$am[which(mtcars$am == 1)] <- 'Manual'
mtcars$am <- as.factor(mtcars$am)

fig <- plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, color = ~am, colors = c('#BF382A', '#0C4B8E'))
fig <- fig %>% add_markers()
fig <- fig %>% layout(scene = list(xaxis = list(title = 'Weight'),
                     yaxis = list(title = 'Gross horsepower'),
                     zaxis = list(title = '1/4 mile time')))

fig
```

### Lung Deaths (Male)

```{r}
library(plotly)
# volcano is a numeric matrix that ships with R
fig <- plot_ly(z = ~volcano)
fig <- fig %>% add_surface()

fig
```
# Lung Deaths {data-icon="fa-lungs"}
### Lung Deaths (Female)

```{r}
library(plotly)
library(rjson)

df <- fromJSON(file="https://gist.githubusercontent.com/davenquinn/988167471993bc2ece29/raw/f38d9cb3dd86e315e237fde5d65e185c39c931c2/data.json") 

colors = c('#8dd3c7','#ffffb3','#bebada',
          '#fb8072','#80b1d3','#fdb462',
          '#b3de69','#fccde5','#d9d9d9',
          '#bc80bd','#ccebc5','#ffed6f');

fig <- plot_ly()

for (i in 1:length(df)) {
  l = c()
  m = c()
  n = c()

  for (j in 1:length(df[[i]])) {
    l[[j]] <- df[[i]][[j]]$clay
    m[[j]] <- df[[i]][[j]]$sand
    n[[j]] <- df[[i]][[j]]$silt
  }

 fig <- add_trace(
    fig,
    type = 'scatterternary',
    a = l,
    b = m,
    c = n,
    name = names(df[i]),
    mode = 'lines',
    line = list(
      color='#444'
    ),
    fill = 'toself',
    fillcolor = colors[i],
    showlegend = F
    )
}

fig <- layout(
  fig,
  title = "Simple Ternary Contour Plot in R",
  ternary = list(
    sum = 100,
    aaxis = list(
      title = "clay",
      ticksuffix = "%",
      min = 0.01,
      linewidth = 2,
      ticks = "outside"
    ),
    baxis = list(
      title = "sand",
      ticksuffix = "%",
      min = 0.01,
      linewidth = 2,
      ticks = "outside"
    ),
    caxis = list(
      title = "silt",
      ticksuffix = "%",
      min = 0.01,
      linewidth = 2,
      ticks = "outside"
    )
  )
)

fig
```

# Earthquakes {data-icon=fa-globe-americas}

```{r librerias, include=FALSE}
library(flexdashboard)
library(readr)
library(dplyr)
library(leaflet)
library(DT)
library(crosstalk)
```

```{r dataset}
earthquakedata <- read_csv("C:/Users/diego/Desktop/Progra/flex/material/Libro2.csv")
```

##
###
```{r}
earthquakedata %>%
  filter(yr== 1995) %>%
  DT::datatable()
```

### Lugar de cada terremoto

```{r}
earthquakedata %>%
  filter(yr== 1995) %>%
  leaflet() %>% # Add default OpenStreetMap map tiles
  addTiles() %>%
  addMarkers(lng = ~lon,
             lat = ~lat,
             label = ~mag)
```

# Crosstalk

```{r}
eq <- SharedData$new (earthquakedata %>% filter(yr>= 2000))
```



##
###

```{r}
filter_slider("mag","Magnitud",eq,step=0,1,width = 250,column = ~mag)
filter_select("yr","Seleccione el año",eq,group= ~yr, multiple= FALSE )
```


```{r}
eq %>%
  DT::datatable()
```

###

```{r}
eq %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(lng = ~lon,
             lat = ~lat,
             label = ~mag)
```


